---
title: "Col4a5xDO Compiled Bayesian Interval Report"
author: "Yuka Takemon"
date: "11/09/2016"
output: pdf_document
---

```{r setup, include=FALSE}
#setdirectory
setwd("~/Desktop/Col4a5xDO/R_col4a5xdo/qtl/")

#load libraries
library(DOQTL)
library(knitr)
library(pander)

#load appropritate qtl maps 
load("./qtl.GFR.log.C2.192.Rdata")
load("./qtl.log.Alb6WK.192.Rdata")
load("./qtl.log.Alb10WK.192.Rdata")
load("./qtl.log.Alb15WK.192.Rdata")

load("./Hi_qtl.GFR.log.C2.192.Rdata")
load("./Hi_qtl.log.Alb6WK.192.Rdata")
load("./Hi_qtl.log.Alb10WK.192.Rdata")
load("./Hi_qtl.log.Alb15WK.192.Rdata")

load("./qtl.GFR.log.C2.F.Rdata")
load("./qtl.log.Alb6WK.192.F.Rdata")
load("./qtl.log.Alb10WK.192.F.Rdata")
load("./qtl.log.Alb15WK.192.F.Rdata")

load("./qtl.GFR.log.C2.M.Rdata")
load("./qtl.log.Alb6WK.192.M.Rdata")
load("./qtl.log.Alb10WK.192.M.Rdata")
load("./qtl.log.Alb15WK.192.M.Rdata")
```

## Col4a5 x DO Hi QTL 

This is document displays the  bayesian intervals QTL maps for the 1415 Col4a5xDO experiment. In this experiment 192 animals were genotyped by GeneSeek and phenotyped for GFR (C2 model) and Albuminura at 6 ,10, and 15 weeks. QTL maps were generated for each of the prior mentioned models. GFR and Albuminuria data have been log transformed to achieve normal distribution.
The intervals were determined using $H_{a}$ QTL model in which sex is considered an additive covariate. The sex effect is determined by the significant peak in the corresponding the $H_{i}$ model. 
The $H_{i}$ model is determined by the difference between the $H_{f}$ model and the $H_{a}$ mode, and the $H_{f}$ model is the $H_{a}$ including sex as an interactive covariate. Thus the $H_{i}$ model will effectively only show the interactive effects of sex on the QTL model. 

###QTL LOD score linear regresion models:
$H_{0} : y = \mu + \beta_{x} x_{i} + \epsilon_{i}$\
$H_{a} : y = \mu + \beta_{x} x_{i} + \beta_{x} g_{i} + \epsilon_{i}$\
$H_{f} : y = \mu + \beta_{x} x_{i} + \beta_{x} g_{i} + \gamma x_{i} g_{i} + \epsilon_{i}$\
$H_{i} : y = \gamma x_{i} g_{i}$

###Terms:
$H_{0} =$ QTL without covariates.\
$H_{a} =$ QTL with additive covariates.\
$H_{f} =$ QTL with additive covariates and interactive covariates. (Full QTL model)\
$H_{i} =$ QTL interaction.

###Interaction:
$H_{i} = H_{f} - H_{a}$\
$H_{0}$ will cancel out, leaving only the interaction term:\
$y_{i} = \gamma x_{i} g_{i}$

\scriptsize

###Glomerular Filtration Rate QTL Bayesian Intervals:
```{r GFR bayesian intervals, echo = F, include= F}
#list of chr with suggested peaks
GFR_chr <- c(2,4,7,9,10,15,16,19)

#get interval for each sig chr
for (i in GFR_chr[1:length(GFR_chr)]){
  assign(paste("chr_",i, sep=""), bayesint(qtl.GFR.log.C2.192, chr = i))
  }

#add 3 empty columns to each data.frame to match final dimension
for (count in 1:length(mget(ls(pattern = "chr_")))){
  temp <-  mget(ls(pattern = "chr_"))[[count]]
  temp$pos <- as.character(temp$pos)
  temp$cM <- as.character(temp$cM)
  temp$lod.sex.effect <- NA
  temp$p.sex.effect <- NA
  temp$female.lod <- NA
  temp$male.lod <- NA
  temp$bayesian.interval.pos <- NA
  assign(names(mget(ls(pattern = "chr_"))[count]), temp)
}

#Create empty datafarme for final GFR dataframe
GFR_int <- data.frame(matrix(vector(), length(GFR_chr), 14 ,
                dimnames=list(c(), c("peak.marker", "chr", "pos", "cM", "perc.var", "lrs", "lod", "p", "neg.log10.p", "lod.sex.effect","p.sex.effect","female.lod", "male.lod", "bayesian.interval.pos"))),
                stringsAsFactors=F)

#get highest peak.marker for each chr and add to new data frame
for (count in 1:length(mget(ls(pattern = "chr_")))){
  GFR_int[count, ] <- mget(ls(pattern = "chr_"))[[count]][2,]
}

#paste edge of interval to column: bayesian interval
for (count in 1:length(mget(ls(pattern = "chr_")))){
  temp <-  mget(ls(pattern = "chr_"))[[count]]
  GFR_int$bayesian.interval.pos[count] <- paste0(temp$pos[[1]], " - \n", temp$pos[[3]]) 
}

#order final by chr 
GFR_int$chr <- as.numeric(GFR_int$chr)
GFR_int <- GFR_int[order(GFR_int$chr),]

#Add lod of sig sex effect from Hi in chr 10: UNC18427765
Hi.lod <- Hi$lod$A["UNC18427765",]$lod
Hi.p <- Hi$lod$A["UNC18427765",]$p

F.lod <- qtl.GFR.log.C2.F$lod$A["UNC18427765",]$lod
M.lod <- qtl.GFR.log.C2.M$lod$A["UNC18427765",]$lod

GFR_int[GFR_int$peak.marker == "UNC18427765", ][ ,"lod.sex.effect"] <- Hi.lod
GFR_int[GFR_int$peak.marker == "UNC18427765", ][ ,"p.sex.effect"] <- Hi.p
GFR_int[GFR_int$peak.marker == "UNC18427765", ][ ,"female.lod"] <- F.lod
GFR_int[GFR_int$peak.marker == "UNC18427765", ][ ,"male.lod"] <- M.lod

#format to 3 sig digits and remove unnecessary columns
GFR_int <- format(GFR_int, digits = 3)
GFR_int <- GFR_int[,c(2,14,1,3,4,7,8,10:13)]
rownames(GFR_int) <- NULL
colnames(GFR_int) <- c("chr", "bayesian\ninterval\npos","peak\nmarker", "pos", "cM","lod","p","sex\neffect\nlod", "sex\neffect\np","female\nlod","male\nlod")

#split datafram
GFR_int1 <- GFR_int[,c(1:7)]
GFR_int2 <- GFR_int[,c(1:3,8:11)]

```
```{r GFR table, echo = F, include = T}
pander(GFR_int1, caption = "14-week GFR C2 model QTL bayesian interval table.",split.cells = 10, split.table = Inf)
pander(GFR_int2, caption = "14-week GFR C2 model QTL sex effect bayesian interval table .",split.cells = 10, split.table = Inf)
```

###6-Week Albuminuria Bayesian Intervals:
```{r Alb6 bayesian intervals, echo = F, include= F}
#clear chr_ objects
rm( list = ls(pattern = "chr_"))

#list of chr with suggested peaks
Alb6_chr <- c(2,4,5,7,9,11,12,16)

#get interval for each sig chr
for (i in Alb6_chr[1:length(Alb6_chr)]){
  assign(paste("chr_",i, sep=""), bayesint(qtl.log.Alb6WK.192, chr = i))
}

#add 3 empty columns to each data.frame to match final dimension
for (count in 1:length(mget(ls(pattern = "chr_")))){
  temp <-  mget(ls(pattern = "chr_"))[[count]]
  temp$pos <- as.character(temp$pos)
  temp$cM <- as.character(temp$cM)
  temp$lod.sex.effect <- NA
  temp$p.sex.effect <- NA
  temp$female.lod <- NA
  temp$male.lod <- NA
  temp$bayesian.interval.pos <- NA
  assign(names(mget(ls(pattern = "chr_"))[count]), temp)
}

#Create empty datafarme for final GFR dataframe
Alb6_int <- data.frame(matrix(vector(), length(Alb6_chr), 14 ,
                dimnames=list(c(), c("peak.marker", "chr", "pos", "cM", "perc.var", "lrs", "lod", "p", "neg.log10.p", "lod.sex.effect","p.sex.effect","female.lod", "male.lod", "bayesian.interval.pos"))),
                stringsAsFactors=F)

#get highest peak.marker for each chr and add to new data frame
for (count in 1:length(mget(ls(pattern = "chr_")))){
  Alb6_int[count, ] <- mget(ls(pattern = "chr_"))[[count]][2,]
}

#paste edge of interval to column: bayesian interval
for (count in 1:length(mget(ls(pattern = "chr_")))){
  temp <-  mget(ls(pattern = "chr_"))[[count]]
  Alb6_int$bayesian.interval.pos[count] <- paste0(temp$pos[[1]], " - \n", temp$pos[[3]]) 
}

#order final by chr 
Alb6_int$chr <- as.numeric(Alb6_int$chr)
Alb6_int <- Alb6_int[order(Alb6_int$chr),]
Alb6_int <- Alb6_int[,c(2,14,1,3,4,7,8,10:13)]
rownames(Alb6_int) <- NULL
colnames(Alb6_int) <- c("chr", "bayesian\ninterval\npos","peak\nmarker", "pos", "cM","lod","p","sex\neffect\nlod", "sex\neffect\np","female\nlod","male\nlod")

#split datafram
Alb6_int1 <- Alb6_int[,c(1:7)]
Alb6_int2 <- Alb6_int[,c(1:3,8:11)]
```
```{r Alb6 table, echo = F, include = T}
pander(Alb6_int1, caption = "6-week albuminuria QTL bayesian interval table.",split.cells = 10, split.table = Inf)
pander(Alb6_int2, caption = "6-week albuminuria QTL sex effect bayesian interval table.",split.cells = 10, split.table = Inf)
```

###10-Week Albuminuria Bayesian Intervals:
```{r Alb10 bayesian intervals, echo = F, include= F}
#clear chr_ objects
rm( list = ls(pattern = "chr_"))

#list of chr with suggested peaks
Alb10_chr <- c(2,4,11,13)

#get interval for each sig chr
for (i in Alb10_chr[1:length(Alb10_chr)]){
  assign(paste("chr_",i, sep=""), bayesint(qtl.log.Alb10WK.192, chr = i))
}

#add 3 empty columns to each data.frame to match final dimension
for (count in 1:length(mget(ls(pattern = "chr_")))){
  temp <-  mget(ls(pattern = "chr_"))[[count]]
  temp$pos <- as.character(temp$pos)
  temp$cM <- as.character(temp$cM)
  temp$lod.sex.effect <- NA
  temp$p.sex.effect <- NA
  temp$female.lod <- NA
  temp$male.lod <- NA
  temp$bayesian.interval.pos <- NA
  assign(names(mget(ls(pattern = "chr_"))[count]), temp)
}

#Create empty datafarme for final GFR dataframe
Alb10_int <- data.frame(matrix(vector(), length(Alb10_chr), 14 ,
                dimnames=list(c(), c("peak.marker", "chr", "pos", "cM", "perc.var", "lrs", "lod", "p", "neg.log10.p", "lod.sex.effect","p.sex.effect","female.lod", "male.lod", "bayesian.interval.pos"))),
                stringsAsFactors=F)

#get highest peak.marker for each chr and add to new data frame
for (count in 1:length(mget(ls(pattern = "chr_")))){
  Alb10_int[count, ] <- mget(ls(pattern = "chr_"))[[count]][2,]
}

#paste edge of interval to column: bayesian interval
for (count in 1:length(mget(ls(pattern = "chr_")))){
  temp <-  mget(ls(pattern = "chr_"))[[count]]
  Alb10_int$bayesian.interval.pos[count] <- paste0(temp$pos[[1]], " - \n", temp$pos[[3]]) 
}

#order final by chr 
Alb10_int$chr <- as.numeric(Alb10_int$chr)
Alb10_int <- Alb10_int[order(Alb10_int$chr),]
Alb10_int <- Alb10_int[,c(2,14,1,3,4,7,8,10:13)]
rownames(Alb10_int) <- NULL
colnames(Alb6_int) <- c("chr", "bayesian\ninterval\npos","peak\nmarker", "pos", "cM","lod","p","sex\neffect\nlod", "sex\neffect\np","female\nlod","male\nlod")

#split datafram
Alb10_int1 <- Alb10_int[,c(1:7)]
Alb10_int2 <- Alb10_int[,c(1:3,8:11)]
```
```{r Alb10 table, echo = F, include = T}
pander(Alb10_int1, caption = "10-week albuminuria QTL bayesian interval table.",split.cells = 10, split.table = Inf)
pander(Alb10_int2, caption = "10-week albuminuria QTL sex effect bayesian interval table.",split.cells = 10, split.table = Inf)
```

###15-Week Albuminuria Bayesian Intervals:
```{r Alb15 bayesian intervals, echo = F, include= F}
#clear chr_ objects
rm( list = ls(pattern = "chr_"))

#list of chr with suggested peaks
Alb15_chr <- c(15)

#get interval for each sig chr
for (i in Alb15_chr[1:length(Alb15_chr)]){
  assign(paste("chr_",i, sep=""), bayesint(qtl.log.Alb15WK.192, chr = i))
}

#add 3 empty columns to each data.frame to match final dimension
for (count in 1:length(mget(ls(pattern = "chr_")))){
  temp <-  mget(ls(pattern = "chr_"))[[count]]
  temp$pos <- as.character(temp$pos)
  temp$cM <- as.character(temp$cM)
  temp$lod.sex.effect <- NA
  temp$p.sex.effect <- NA
  temp$female.lod <- NA
  temp$male.lod <- NA
  temp$bayesian.interval.pos <- NA
  assign(names(mget(ls(pattern = "chr_"))[count]), temp)
}

#Create empty datafarme for final GFR dataframe
Alb15_int <- data.frame(matrix(vector(), length(Alb15_chr), 14 ,
                dimnames=list(c(), c("peak.marker", "chr", "pos", "cM", "perc.var", "lrs", "lod", "p", "neg.log10.p", "lod.sex.effect","p.sex.effect","female.lod", "male.lod", "bayesian.interval.pos"))),
                stringsAsFactors=F)

#get highest peak.marker for each chr and add to new data frame
for (count in 1:length(mget(ls(pattern = "chr_")))){
  Alb15_int[count, ] <- mget(ls(pattern = "chr_"))[[count]][2,]
}

#paste edge of interval to column: bayesian interval
for (count in 1:length(mget(ls(pattern = "chr_")))){
  temp <-  mget(ls(pattern = "chr_"))[[count]]
  Alb15_int$bayesian.interval.pos[count] <- paste0(temp$pos[[1]], " - \n", temp$pos[[3]]) 
}

#order final by chr 
Alb15_int$chr <- as.numeric(Alb15_int$chr)
Alb15_int <- Alb15_int[order(Alb15_int$chr),]
Alb15_int <- Alb15_int[,c(2,14,1,3,4,7,8,10:13)]
rownames(Alb15_int) <- NULL
colnames(Alb6_int) <- c("chr", "bayesian\ninterval\npos","peak\nmarker", "pos", "cM","lod","p","sex\neffect\nlod", "sex\neffect\np","female\nlod","male\nlod")

#split datafram
Alb15_int1 <- Alb15_int[,c(1:7)]
Alb15_int2 <- Alb15_int[,c(1:3,8:11)]
```
```{r Alb15 table, echo = F, include = T}
pander(Alb15_int1, caption = "15-week albuminuria QTL bayesian interval table.",split.cells = 10, split.table = Inf)
pander(Alb15_int2, caption = "15-week albuminuria QTL sex effect bayesian interval table.",split.cells = 10, split.table = Inf)
```